# Swirl Practice
#### Exercise 1:
Sum of numbers
```{r}
sum(2000:20000)
```

#### Exercise 2:
Objects

```{r}
a <- 5
b <- 2:20
a
b
```

* line 1 initializes variable a with integer value 5, and line 2 initializes variable b with vector containing values from 2 to 20 inclusive (ie. 2, 3, 4, 5... 19, 20)

* line 3 prints variable a, and line 4 prints variable b

#### Exercise 3:

```
d <- "I just want to be deleted"
d
ls() #note that you have to include the parentheses for a function even if no arguments are needed.
rm(d)
ls()
d #generates an error because we removed it
```

Using '+'
```{r}
c <- a + b
c
```
Using 'sum()'
```{r}
c <- sum(a, b)
c
```
We get different results because + adds 5 to all elements in the vector b while sum() adds 5 and all elements in vector b together to get one integer output. 

#### Exercise 4
Sum of 5th and 10th element of vector b
```{r}
sum(b[c(5, 10)])
```
#### Exercise 5
Sum of 3rd, 8th, and 10th element of b
```{r}
sum(b[c(3, 8, 10)])
```

#### Exercise 6 
```{r}
m <- matrix(data=1:25,ncol=5,byrow=T)
m
m[5,5]
```

* First number is rows, second is coloumns

* m[3,] will print out the 3rd row of matrix m
```{r}
m[3,]
```
Extract 3rd, 4th, and 5th column of m together as one object
```{r}
m[,c(3, 4, 5)]
```

#### Exercise 7
```{r}
cbind(m, 101:105)
```
* cbind combines matrices, vectors, and dataframes by coloumns
* rbind does the samething but for rows
```{r}
m
n <- rbind(rep(0, 5), m)
n
```









